---
title: "Patrol Divison Overview, as of `r format(Sys.Date() - 4, '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    logo: Y:/Projects/dashboard/RPDCrimeDashboard/Objects/RPDLogoSMALL.png
    orientation: row
    vertical_layout: fill
    theme: cerulean
---

```{r loaddata}

curr.year <- as.numeric(format(Sys.Date(), '%Y')) ### This current year to automatically reference the current year
begindate <- paste0(curr.year, '-01-01') ### For CFS to automatically create the begindate based on current year

library(tidyverse)
library(stringr)
library(knitr)
library(flexdashboard)
library(RColorBrewer)
library(plotly)
library(leaflet)
library(reshape2)
library(jsonlite)
library(DT)
library(RODBC)
library(mapview) #for cool popups
library(leaflet.extras) #for popups in GeoJSON objects

source("Y:/Projects/dashboard/RPDCrimeDashboard/Functions/LERMS_incidents.R")
source("Y:/Projects/dashboard/RPDCrimeDashboard/Functions/SPC.R")
source("Y:/Projects/dashboard/RPDCrimeDashboard/Functions/pullMCUdata.R")
source("Y:/Projects/dashboard/RPDCrimeDashboard/Functions/loadshootingvictims.R")

overviewmapfunc <- function(daddyJSON, 
                            lakeSPC, 
                            geneseeSPC, 
                            goodmanSPC, 
                            clintonSPC, 
                            centralSPC,
                            linkhash,
                            citymap,
                            sec) {
    babyJSON <- daddyJSON
    crimediff <- data_frame("Section" = sec,
                            "Difference" = c(lakeSPC[[2]] - lakeSPC[[3]],
                                             geneseeSPC[[2]] - geneseeSPC[[3]],
                                             goodmanSPC[[2]] - goodmanSPC[[3]],
                                             clintonSPC[[2]] - clintonSPC[[3]],
                                             centralSPC[[2]] - centralSPC[[3]])
                            ) %>%
        mutate(fillOpacity = abs(Difference / 100),
               fillColor = case_when(.$Difference > 0 ~ "Red",
                                     .$Difference < 0 ~ "Green",
                                     TRUE ~ "White"))
    
    crimediff <- crimediff[match(lapply(babyJSON$features, 
                                        function(x) x$properties$Section) %>% 
                                     unlist(), 
                                 crimediff$Section),]
    babyJSON$features <- lapply(
        babyJSON$features, function(x) {
            x$properties$style <- list(
                fillColor = crimediff$fillColor[which(
                    crimediff$Section == x$properties$Section)],
                fillOpacity = crimediff$fillOpacity[which(
                    crimediff$Section == x$properties$Section)]
            )
            x
        }
    )
    
    links <- data_frame(Section = sec,
                        link = c(paste0('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/LakeCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Lake Section Dashboard</a>'), 
                                 paste0('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/GeneseeCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Genesee Section Dashboard</a>'), 
                                 paste0('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/GoodmanCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Goodman Section Dashboard</a>'), 
                                 paste0('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/ClintonCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Clinton Section Dashboard</a>'), 
                                 paste0('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/CentralCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Central Section Dashboard</a>')))
    
    babyJSON$features <- lapply(babyJSON$features, function(x) {
        
        x$properties$popup = links$link[which(links$Section == x$properties$Section)]
        x
    })
    
    return(citymap %>%
               addGeoJSON(
                   babyJSON
               ) %>%
               addGeoJSONv2(
                   babyJSON,
                   fillOpacity = 0,
                   popupProperty = "popup",
                   labelProperty = "Section",
                   highlightOptions = highlightOptions(color = 'white', weight = 10, bringToFront = TRUE)
               ))
    
}

simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), tolower(substring(s, 2)),
      sep="", collapse=" ")
}

daddyJSON <- readLines("https://opendata.arcgis.com/datasets/772f3621fa354ec9abf3ba33f3ace59e_0.geojson") %>%
    paste(collapse = "\n") %>%
    fromJSON(simplifyVector = FALSE)
#gather section names and set color palettes for sections and beats
secNames <- sapply(daddyJSON$features, function(x) x$properties$Section)
sectionpal <- colorFactor(palette = colorspace::sequential_hcl(5),
                          domain = secNames)

citymap <- readRDS(file = "Z:/Projects/dashboard/RPDCrimeDashboard/Objects/citymap.RDS")
#old fitbounds: fitBounds(lng1 = -77.55, lat1 = 43.11, lng2 = -77.668684, lat2 = 43.264020)

#sevenDayGroupTable is a lookup table to get the current week (Group) from the date
#Because it uses length(Date) from seq.Date, it should work even in leap years

sevenDayGroupTable <- data.frame(Date = seq.Date(from = as.Date(begindate),
                                                 to = as.Date(paste0(curr.year, "-12-31")),
                                                 by = 1)) %>%
    mutate(DOY = 1:length(Date),
           Group = c(rep(1:51, each = 7), 
                     rep(52, times = length(Date) - 357)))

curr.week <- sevenDayGroupTable$Group[match(as.numeric(format(Sys.Date(), 
                                                             '%j')), 
                                           sevenDayGroupTable$DOY)] - 1

firearm.desc <- trimws(c('Prohibited Use of Weapon City Limits', 
                        'Use of Dangerous Weapon', 
                        'Criminal Use Firearm 1st: Commit Violent Class B Felony', 
                        'Discharges Loaded Firearm', 
                        'Use Firearm 1st: Possess a Deadly Weapon-Loaded',
                        'Criminal Use Firearm 2nd: Possess Deadly Weapon: Loaded', 
                        'Use Firearm 1st: Display Firearm', 
                        'Criminal Use Firearm 2nd: Display Firearm'))

firearmCrimeTypes <- c("Aggravated Assault", "Robbery", "Homicide", "Rape", "Simple Assault")

#load in RPD's crime data

df <- readRDS(file = "Z:/Projects/dashboard/RPDCrimeDashboard/Objects/citywidedf.RDS")

#use beatNames to make factor levels for beats
beatNames <- df %>%
    select(GEOBeat) %>%
    unique() %>% 
    filter(! grepl(x = GEOBeat, pattern = "\\*")) %>% #remove *** as a beat name
    arrange(substr(GEOBeat, 3, 3), GEOBeat) %>%
    mutate(GEOBeat = as.factor(GEOBeat)) #this keeps *** as a factor level

CPWs <- df %>% filter(CrimeType == "Dangerous Weapons" & 
                          !trimws(Description) %in% firearm.desc &
                          as.numeric(WeaponIBRValue) < 11) %>%
    mutate(OccurFromDate = as.character(OccurFromDate)) #for table display purposes

crimes <- c('Aggravated Assault', 'Arson', 'Burglary', 'Homicide', 'Larceny', 'MV Theft', 'Rape', 'Robbery', 'Firearm')
sec <- c('Lake', 'Genesee', 'Goodman', 'Clinton', 'Central')

pal <- brewer.pal(name = "Reds", n = 9)

PropVals <- read.csv("Y:/Projects/dashboard/RPDCrimeDashboard/Objects/ProportionsAndCounts.csv",
                     header= T)
ShootingControlLimits <- read.csv("Y:/Projects/dashboard/RPDCrimeDashboard/Objects/3YrWeightedControlLimitsShootings.csv")
ShootingProps <- read.csv("Y:/Projects/dashboard/RPDCrimeDashboard/Objects/ProportionsAndCountsShootings.csv",
                          stringsAsFactors = FALSE)
ShootingPropsFull <- ShootingProps

histdata <- read.csv(file = "Y:/Projects/dashboard/RPDCrimeDashboard/Objects/historicaldata.csv",
                     stringsAsFactors = FALSE,
                     header = TRUE)

controllimits <- read.csv(file = "Y:/Projects/dashboard/RPDCrimeDashboard/Objects/3YrWeightedControlLimits.csv", 
                       header = TRUE)

controllimits <- rbind(data.frame(controllimits, Year = 2017),
                    data.frame(controllimits, Year = 2018),
                    data.frame(controllimits, Year = 2019))
# 
# mculist <- pullMCUdata()
# MCUhoms <- mculist[[1]]
# person <- mculist[[2]]
# rm(mculist)
# MCUhoms <- MCUhoms %>%
#     mutate(CrimeType = "Homicide",
#            DateOfEvent = as.Date(DateOfEvent, format = "%Y-%m-%d"),
#            DOYofEvent = as.numeric(format(DateOfEvent, "%j")),
#            YearofEvent = as.numeric(format(DateOfEvent, "%Y")),
#            CaseStatus = unname(sapply(CaseStatus, simpleCap))) %>%
#     filter(YearofEvent == curr.year) %>%
#     dplyr::rename(sec = Section,
#                   Lat = Latitude,
#                   Lon = Longitude,
#                   FullAddress = Address) %>%
#     left_join(sevenDayGroupTable, by = c("DOYofEvent" = "DOY")) %>%
#     select(-Date) %>%
#     dplyr::rename("SevenDaysGroup" = Group)
# 
# personincident <- left_join(MCUhoms, person, by = "CaseNumber")
# 
# sv <- loadshootingvictims()
# drops <- c("Lat", "Lon")
# svjoined <- left_join(x = sv, y = df, by = c("CaseNumber" = "CRNum")) %>%
#     select(-one_of(drops)) %>%
#     rename(Lat = Latitude, Lon = Longitude)

```

```{r SPC, eval=FALSE}

PropValsLake <- filter(PropVals, Section == "Lake")
PropValsGenesee <- filter(PropVals, Section == "Genesee")
PropValsGoodman <- filter(PropVals, Section == "Goodman")
PropValsClinton <- filter(PropVals, Section == "Clinton")
PropValsCentral <- filter(PropVals, Section == "Central")

df.Lake <- filter(df, sec == "Lake")
df.Genesee <- filter(df, sec == "Genesee")
df.Goodman <- filter(df, sec == "Goodman")
df.Clinton <- filter(df, sec == "Clinton")
df.Central <- filter(df, sec == "Central")

firearmSPC.Lake <- SPC(crimetype = "Firearm", Prop.Vals = PropValsLake, dataf = df.Lake)
firearmSPC.Genesee <- SPC(crimetype = "Firearm", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
firearmSPC.Goodman <- SPC(crimetype = "Firearm", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
firearmSPC.Clinton <- SPC(crimetype = "Firearm", Prop.Vals = PropValsClinton, dataf = df.Clinton)
firearmSPC.Central <- SPC(crimetype = "Firearm", Prop.Vals = PropValsCentral, dataf = df.Central)

ShootingProps <- filter(ShootingPropsFull, Section == "Lake") #To avoid having to change the SPC function...
svSPC.Lake <- SPC(crimetype = "Shooting", dataf = filter(svjoined, sec == "Lake"))
ShootingProps <- filter(ShootingPropsFull, Section == "Genesee")
svSPC.Genesee <- SPC(crimetype = "Shooting", dataf = filter(svjoined, sec == "Genesee"))
ShootingProps <- filter(ShootingPropsFull, Section == "Goodman")
svSPC.Goodman <- SPC(crimetype = "Shooting", dataf = filter(svjoined, sec == "Goodman"))
ShootingProps <- filter(ShootingPropsFull, Section == "Clinton")
svSPC.Clinton <- SPC(crimetype = "Shooting", dataf = filter(svjoined, sec == "Clinton"))
ShootingProps <- filter(ShootingPropsFull, Section == "Central")
svSPC.Central <- SPC(crimetype = "Shooting", dataf = filter(svjoined, sec == "Central"))

homicideSPC.Lake <- SPC(crimetype = "Homicide", Prop.Vals = PropValsLake, dataf = df.Lake)
homicideSPC.Genesee <- SPC(crimetype = "Homicide", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
homicideSPC.Goodman <- SPC(crimetype = "Homicide", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
homicideSPC.Clinton <- SPC(crimetype = "Homicide", Prop.Vals = PropValsClinton, dataf = df.Clinton)
homicideSPC.Central <- SPC(crimetype = "Homicide", Prop.Vals = PropValsCentral, dataf = df.Central)

rapeSPC.Lake <- SPC(crimetype = "Rape", Prop.Vals = PropValsLake, dataf = df.Lake)
rapeSPC.Genesee <- SPC(crimetype = "Rape", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
rapeSPC.Goodman <- SPC(crimetype = "Rape", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
rapeSPC.Clinton <- SPC(crimetype = "Rape", Prop.Vals = PropValsClinton, dataf = df.Clinton)
rapeSPC.Central <- SPC(crimetype = "Rape", Prop.Vals = PropValsCentral, dataf = df.Central)

robSPC.Lake <- SPC(crimetype = "Robbery", Prop.Vals = PropValsLake, dataf = df.Lake)
robSPC.Genesee <- SPC(crimetype = "Robbery", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
robSPC.Goodman <- SPC(crimetype = "Robbery", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
robSPC.Clinton <- SPC(crimetype = "Robbery", Prop.Vals = PropValsClinton, dataf = df.Clinton)
robSPC.Central <- SPC(crimetype = "Robbery", Prop.Vals = PropValsCentral, dataf = df.Central)

asltSPC.Lake <- SPC(crimetype = "Aggravated Assault", Prop.Vals = PropValsLake, dataf = df.Lake)
asltSPC.Genesee <- SPC(crimetype = "Aggravated Assault", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
asltSPC.Goodman <- SPC(crimetype = "Aggravated Assault", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
asltSPC.Clinton <- SPC(crimetype = "Aggravated Assault", Prop.Vals = PropValsClinton, dataf = df.Clinton)
asltSPC.Central <- SPC(crimetype = "Aggravated Assault", Prop.Vals = PropValsCentral, dataf = df.Central)

burgSPC.Lake <- SPC(crimetype = "Burglary", Prop.Vals = PropValsLake, dataf = df.Lake)
burgSPC.Genesee <- SPC(crimetype = "Burglary", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
burgSPC.Goodman <- SPC(crimetype = "Burglary", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
burgSPC.Clinton <- SPC(crimetype = "Burglary", Prop.Vals = PropValsClinton, dataf = df.Clinton)
burgSPC.Central <- SPC(crimetype = "Burglary", Prop.Vals = PropValsCentral, dataf = df.Central)

larcSPC.Lake <- SPC(crimetype = "Larceny", Prop.Vals = PropValsLake, dataf = df.Lake)
larcSPC.Genesee <- SPC(crimetype = "Larceny", Prop.Vals = PropValsGenesee, dataf = df.Genesee)
larcSPC.Goodman <- SPC(crimetype = "Larceny", Prop.Vals = PropValsGoodman, dataf = df.Goodman)
larcSPC.Clinton <- SPC(crimetype = "Larceny", Prop.Vals = PropValsClinton, dataf = df.Clinton)
larcSPC.Central <- SPC(crimetype = "Larceny", Prop.Vals = PropValsCentral, dataf = df.Central)

```

```{r loadSPC}

sectionSPClist <- readRDS("Z:/Projects/dashboard/RPDCrimeDashboard/Objects/sectionSPClist.RDS")

```

```{r ylims}

mins <- histdata %>% 
    group_by(CrimeType) %>% 
    arrange(Counts) %>% 
    filter(rank(Counts, ties.method = "first") == 1) %>%
    ungroup()
maxes <- histdata %>% 
    group_by(CrimeType) %>% 
    arrange(Counts) %>% 
    filter(rank(Counts, ties.method = "first") == 40) %>% #5 sections, 8 years, 40 possible values
    ungroup()
```

Firearm Crime {data-navmenu="Violent Crime"} 
======================================================================

> Firearm Crime

Row
------------------------------------------------------------------------------

### Section comparison

```{r firearmtable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Firearm[[4]],
                             sectionSPClist$Genesee$Firearm[[4]],
                             sectionSPClist$Goodman$Firearm[[4]],
                             sectionSPClist$Clinton$Firearm[[4]],
                             sectionSPClist$Central$Firearm[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Firearm[[2]],
                                sectionSPClist$Genesee$Firearm[[2]],
                                sectionSPClist$Goodman$Firearm[[2]],
                                sectionSPClist$Clinton$Firearm[[2]],
                                sectionSPClist$Central$Firearm[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Firearm[[3]],
                                    sectionSPClist$Genesee$Firearm[[3]],
                                    sectionSPClist$Goodman$Firearm[[3]],
                                    sectionSPClist$Clinton$Firearm[[3]],
                                    sectionSPClist$Central$Firearm[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))
```

### Map

```{r Firearmcrimemap}

firearmsJSON <- daddyJSON

firearmdiff <- data_frame("Section" = sec,
                          "Difference" = c(sectionSPClist$Lake$Firearm[[2]] - sectionSPClist$Lake$Firearm[[3]],
                                           sectionSPClist$Genesee$Firearm[[2]] - sectionSPClist$Genesee$Firearm[[3]],
                                           sectionSPClist$Goodman$Firearm[[2]] - sectionSPClist$Goodman$Firearm[[3]],
                                           sectionSPClist$Clinton$Firearm[[2]] - sectionSPClist$Clinton$Firearm[[3]],
                                           sectionSPClist$Central$Firearm[[2]] - sectionSPClist$Central$Firearm[[3]])) %>%
    mutate(fillOpacity = abs(Difference / 100),
           fillColor = case_when(.$Difference > 0 ~ "Red",
                             .$Difference < 0 ~ "Green",
                             TRUE ~ "White"))
firearmdiff <- firearmdiff[match(lapply(firearmsJSON$features, function(x) x$properties$Section) %>% 
                                     unlist(), 
                                 firearmdiff$Section),]

firearmsJSON$features <- lapply(firearmsJSON$features, function(x) {
    x$properties$style <- list(
        fillColor = firearmdiff$fillColor[which(firearmdiff$Section == x$properties$Section)],
        fillOpacity = firearmdiff$fillOpacity[which(firearmdiff$Section == x$properties$Section)]
    )
    x
})

links <- data_frame(Section = sec,
                    link = c('<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/LakeCrimeDashboard.html#firearm-crime-1" target="_blank">Lake Section Dashboard</a>', 
                             '<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/GeneseeCrimeDashboard.html#firearm-crime-1" target="_blank">Genesee Section Dashboard</a>', 
                             '<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/GoodmanCrimeDashboard.html#firearm-crime-1" target="_blank">Goodman Section Dashboard</a>', 
                             '<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/ClintonCrimeDashboard.html#firearm-crime-1" target="_blank">Clinton Section Dashboard</a>', 
                             '<a href="file://rpdfs.cor.local/mcac$/MCAC Operations/Crime Dashboards/CentralCrimeDashboard.html#firearm-crime-1" target="_blank">Central Section Dashboard</a>'))


firearmsJSON$features <- lapply(firearmsJSON$features, function(x) {
    
    x$properties$popup = links$link[which(links$Section == x$properties$Section)]
    x
})

citymap %>%
    addGeoJSON(
        firearmsJSON
        ) %>%
    addGeoJSONv2(
        firearmsJSON
        , fillOpacity = 0
        , popupProperty = "popup"
        , labelProperty = "Section"
        , highlightOptions = highlightOptions(color = "white", weight = 10, bringToFront = TRUE)
        )

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
firearmcontrol <- filter(controllimits, Crime == "Firearm")
SimsAvg <- mean(sectionSPClist$Lake$Firearm[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Firearm") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- firearmcontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Firearm") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- firearmcontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0


p <- ggplot(filter(histdata, CrimeType == "Firearm", Section == 1), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(firearmcontrol, Section == 'Lake'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(firearmcontrol, Section == 'Lake'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Firearm[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
    
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
firearmcontrol <- filter(controllimits, Crime == "Firearm")
SimsAvg <- mean(sectionSPClist$Genesee$Firearm[[5]]$Value)

p <- ggplot(filter(histdata, CrimeType == "Firearm", Section == 3), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(firearmcontrol, Section == 'Genesee'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(firearmcontrol, Section == 'Genesee'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Firearm[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
    
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
firearmcontrol <- filter(controllimits, Crime == "Firearm")
SimsAvg <- mean(sectionSPClist$Goodman$Firearm[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Firearm", Section == 5), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(firearmcontrol, Section == 'Goodman'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(firearmcontrol, Section == 'Goodman'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Firearm[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
    
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
firearmcontrol <- filter(controllimits, Crime == "Firearm")
SimsAvg <- mean(sectionSPClist$Clinton$Firearm[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Firearm", Section == 7), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(firearmcontrol, Section == 'Clinton'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(firearmcontrol, Section == 'Clinton'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Firearm[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
    
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
firearmcontrol <- filter(controllimits, Crime == "Firearm")
SimsAvg <- mean(sectionSPClist$Central$Firearm[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Firearm", Section == 9), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(firearmcontrol, Section == 'Central'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(firearmcontrol, Section == 'Central'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Firearm[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
    
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

Shooting Victims{data-navmenu="Violent Crime"} 
======================================================================

> Shooting Victims

Row
------------------------------------------------------------------------------

### Section comparison

```{r shootingvictimstables}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$SV[[4]],
                             sectionSPClist$Genesee$SV[[4]],
                             sectionSPClist$Goodman$SV[[4]],
                             sectionSPClist$Clinton$SV[[4]],
                             sectionSPClist$Central$SV[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$SV[[2]],
                                sectionSPClist$Genesee$SV[[2]],
                                sectionSPClist$Goodman$SV[[2]],
                                sectionSPClist$Clinton$SV[[2]],
                                sectionSPClist$Central$SV[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$SV[[3]],
                                    sectionSPClist$Genesee$SV[[3]],
                                    sectionSPClist$Goodman$SV[[3]],
                                    sectionSPClist$Clinton$SV[[3]],
                                    sectionSPClist$Central$SV[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r svmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$SV,
                geneseeSPC = sectionSPClist$Genesee$SV,
                goodmanSPC = sectionSPClist$Goodman$SV,
                clintonSPC = sectionSPClist$Clinton$SV,
                centralSPC = sectionSPClist$Central$SV,
                linkhash = "#shooting-victims-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
SimsAvg <- mean(sectionSPClist$Lake$SV[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Shooting") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- ShootingControlLimits %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Shooting") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- ShootingControlLimits %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Shooting", Section == 1), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    theme_bw() +
    geom_line(data = filter(ShootingControlLimits, Section == 'Lake'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(ShootingControlLimits, Section == 'Lake'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    geom_point(data = sectionSPClist$Lake$SV[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
SimsAvg <- mean(sectionSPClist$Genesee$SV[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Shooting", Section == 3), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(ShootingControlLimits, Section == 'Genesee'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(ShootingControlLimits, Section == 'Genesee'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$SV[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
SimsAvg <- mean(sectionSPClist$Goodman$SV[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Shooting", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(ShootingControlLimits, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(ShootingControlLimits, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$SV[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
SimsAvg <- mean(sectionSPClist$Clinton$SV[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Shooting", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(ShootingControlLimits, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(ShootingControlLimits, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$SV[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
SimsAvg <- mean(sectionSPClist$Central$SV[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Shooting", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(ShootingControlLimits, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(ShootingControlLimits, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$SV[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

Robbery {data-navmenu="Violent Crime"} 
======================================================================

> Robbery

Row
------------------------------------------------------------------------------

### Section comparison

```{r robberytable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Rob[[4]],
                             sectionSPClist$Genesee$Rob[[4]],
                             sectionSPClist$Goodman$Rob[[4]],
                             sectionSPClist$Clinton$Rob[[4]],
                             sectionSPClist$Central$Rob[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Rob[[2]],
                                sectionSPClist$Genesee$Rob[[2]], 
                                sectionSPClist$Goodman$Rob[[2]], 
                                sectionSPClist$Clinton$Rob[[2]], 
                                sectionSPClist$Central$Rob[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Rob[[3]],
                                    sectionSPClist$Genesee$Rob[[3]],
                                    sectionSPClist$Goodman$Rob[[3]],
                                    sectionSPClist$Clinton$Rob[[3]],
                                    sectionSPClist$Central$Rob[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```                         

### Map

```{r robmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Rob,
                geneseeSPC = sectionSPClist$Genesee$Rob,
                goodmanSPC = sectionSPClist$Goodman$Rob,
                clintonSPC = sectionSPClist$Clinton$Rob,
                centralSPC = sectionSPClist$Central$Rob,
                linkhash = "#robbery-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
robcontrol <- filter(controllimits, Crime == "Robbery")
SimsAvg <- mean(sectionSPClist$Lake$Rob[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Robbery") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- robcontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Robbery") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- robcontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Robbery", Section == 1), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(robcontrol, Section == 'Lake'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(robcontrol, Section == 'Lake'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Rob[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
robcontrol <- filter(controllimits, Crime == "Robbery")
SimsAvg <- mean(sectionSPClist$Genesee$Rob[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Robbery", Section == 3), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(robcontrol, Section == 'Genesee'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(robcontrol, Section == 'Genesee'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Rob[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
robcontrol <- filter(controllimits, Crime == "Robbery")
SimsAvg <- mean(sectionSPClist$Goodman$Rob[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Robbery", Section == 5), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(robcontrol, Section == 'Goodman'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(robcontrol, Section == 'Goodman'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Rob[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
robcontrol <- filter(controllimits, Crime == "Robbery")
SimsAvg <- mean(sectionSPClist$Clinton$Rob[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Robbery", Section == 7), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(robcontrol, Section == 'Clinton'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(robcontrol, Section == 'Clinton'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Rob[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
robcontrol <- filter(controllimits, Crime == "Robbery")
SimsAvg <- mean(sectionSPClist$Central$Rob[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Robbery", Section == 9), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(robcontrol, Section == 'Central'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(robcontrol, Section == 'Central'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Rob[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

Aggravated Assaults {data-navmenu="Violent Crime"} 
======================================================================

> Aggravated Assaults

Row
------------------------------------------------------------------------------

### Section comparison

```{r aggassaulttable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Aslt[[4]],
                             sectionSPClist$Genesee$Aslt[[4]],
                             sectionSPClist$Goodman$Aslt[[4]],
                             sectionSPClist$Clinton$Aslt[[4]],
                             sectionSPClist$Central$Aslt[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Aslt[[2]],
                                sectionSPClist$Genesee$Aslt[[2]],
                                sectionSPClist$Goodman$Aslt[[2]],
                                sectionSPClist$Clinton$Aslt[[2]],
                                sectionSPClist$Central$Aslt[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Aslt[[3]],
                                    sectionSPClist$Genesee$Aslt[[3]],
                                    sectionSPClist$Goodman$Aslt[[3]],
                                    sectionSPClist$Clinton$Aslt[[3]],
                                    sectionSPClist$Central$Aslt[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r asltmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Aslt,
                geneseeSPC = sectionSPClist$Genesee$Aslt,
                goodmanSPC = sectionSPClist$Goodman$Aslt,
                clintonSPC = sectionSPClist$Clinton$Aslt,
                centralSPC = sectionSPClist$Central$Aslt,
                linkhash = "#aggravated-assault-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
asltcontrol <- filter(controllimits, Crime == "Aggravated Assault")
SimsAvg <- mean(sectionSPClist$Lake$Aslt[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Aggravated Assault") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- asltcontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Aggravated Assault") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- asltcontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0


p <- ggplot(filter(histdata, CrimeType == "Aggravated Assault", Section == 1), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    theme_bw() +
    geom_line(data = filter(asltcontrol, Section == 'Lake'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(asltcontrol, Section == 'Lake'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    geom_point(data = sectionSPClist$Lake$Aslt[[5]], 
               aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
asltcontrol <- filter(controllimits, Crime == "Aggravated Assault")
SimsAvg <- mean(sectionSPClist$Genesee$Aslt[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Aggravated Assault", Section == 3), aes(x = Yr, y = Counts)) +
    geom_line() +
    theme_bw() +
    geom_line(data = filter(asltcontrol, Section == 'Genesee'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(asltcontrol, Section == 'Genesee'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    geom_point(data = sectionSPClist$Genesee$Aslt[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
asltcontrol <- filter(controllimits, Crime == "Aggravated Assault")
SimsAvg <- mean(sectionSPClist$Goodman$Aslt[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Aggravated Assault", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(asltcontrol, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(asltcontrol, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Aslt[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
asltcontrol <- filter(controllimits, Crime == "Aggravated Assault")
SimsAvg <- mean(sectionSPClist$Clinton$Aslt[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Aggravated Assault", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(asltcontrol, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(asltcontrol, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Aslt[[5]], 
               aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
asltcontrol <- filter(controllimits, Crime == "Aggravated Assault")
SimsAvg <- mean(sectionSPClist$Central$Aslt[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Aggravated Assault", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(asltcontrol, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(asltcontrol, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Aslt[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```


Homicide {data-navmenu="Violent Crime"} 
======================================================================

> Homicide

Row
------------------------------------------------------------------------------

### Section comparison

```{r homicidetable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Homicide[[4]],
                             sectionSPClist$Genesee$Homicide[[4]],
                             sectionSPClist$Goodman$Homicide[[4]],
                             sectionSPClist$Clinton$Homicide[[4]],
                             sectionSPClist$Central$Homicide[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Homicide[[2]],
                                sectionSPClist$Genesee$Homicide[[2]],
                                sectionSPClist$Goodman$Homicide[[2]],
                                sectionSPClist$Clinton$Homicide[[2]],
                                sectionSPClist$Central$Homicide[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Homicide[[3]],
                                    sectionSPClist$Genesee$Homicide[[3]],
                                    sectionSPClist$Goodman$Homicide[[3]],
                                    sectionSPClist$Clinton$Homicide[[3]],
                                    sectionSPClist$Central$Homicide[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r hommap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Homicide,
                geneseeSPC = sectionSPClist$Genesee$Homicide,
                goodmanSPC = sectionSPClist$Goodman$Homicide,
                clintonSPC = sectionSPClist$Clinton$Homicide,
                centralSPC = sectionSPClist$Central$Homicide,
                linkhash = "#homicide-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
homcontrol <- filter(controllimits, Crime == "Homicide")
SimsAvg <- mean(sectionSPClist$Lake$Homicide[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Homicide") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- homcontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Homicide") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- homcontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Homicide", Section == 1), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(homcontrol, Section == 'Lake'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(homcontrol, Section == 'Lake'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Homicide[[5]], 
               aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
homcontrol <- filter(controllimits, Crime == "Homicide")
SimsAvg <- mean(sectionSPClist$Genesee$Homicide[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Homicide", Section == 3), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(homcontrol, Section == 'Genesee'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(homcontrol, Section == 'Genesee'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Homicide[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
homcontrol <- filter(controllimits, Crime == "Homicide")
SimsAvg <- mean(sectionSPClist$Goodman$Homicide[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Homicide", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(homcontrol, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(homcontrol, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Homicide[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
homcontrol <- filter(controllimits, Crime == "Homicide")
SimsAvg <- mean(sectionSPClist$Clinton$Homicide[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Homicide", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(homcontrol, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(homcontrol, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Homicide[[5]], 
               aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
homcontrol <- filter(controllimits, Crime == "Homicide")
SimsAvg <- mean(sectionSPClist$Central$Homicide[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Homicide", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(homcontrol, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(homcontrol, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Homicide[[5]], 
               aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

Rape {data-navmenu="Violent Crime"} 
======================================================================

> Rape

Row
------------------------------------------------------------------------------

### Section comparison

```{r rapetable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Rape[[4]],
                             sectionSPClist$Genesee$Rape[[4]],
                             sectionSPClist$Goodman$Rape[[4]],
                             sectionSPClist$Clinton$Rape[[4]],
                             sectionSPClist$Central$Rape[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Rape[[2]],
                                sectionSPClist$Genesee$Rape[[2]],
                                sectionSPClist$Goodman$Rape[[2]],
                                sectionSPClist$Clinton$Rape[[2]],
                                sectionSPClist$Central$Rape[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Rape[[3]],
                                    sectionSPClist$Genesee$Rape[[3]],
                                    sectionSPClist$Goodman$Rape[[3]],
                                    sectionSPClist$Clinton$Rape[[3]],
                                    sectionSPClist$Central$Rape[[3]]))


datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r rapemap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Rape,
                geneseeSPC = sectionSPClist$Genesee$Rape,
                goodmanSPC = sectionSPClist$Goodman$Rape,
                clintonSPC = sectionSPClist$Clinton$Rape,
                centralSPC = sectionSPClist$Central$Rape,
                linkhash = "#rape-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
rapecontrol <- filter(controllimits, Crime == "Rape")
SimsAvg <- mean(sectionSPClist$Lake$Rape[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Rape") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- rapecontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Rape") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- rapecontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Rape", Section == 1), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(rapecontrol, Section == 'Lake'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(rapecontrol, Section == 'Lake'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Rape[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
rapecontrol <- filter(controllimits, Crime == "Rape")
SimsAvg <- mean(sectionSPClist$Genesee$Rape[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Rape", Section == 3), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(rapecontrol, Section == 'Genesee'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(rapecontrol, Section == 'Genesee'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Rape[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
rapecontrol <- filter(controllimits, Crime == "Rape")
SimsAvg <- mean(sectionSPClist$Goodman$Rape[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Rape", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(rapecontrol, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(rapecontrol, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Rape[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
rapecontrol <- filter(controllimits, Crime == "Rape")
SimsAvg <- mean(sectionSPClist$Clinton$Rape[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Rape", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(rapecontrol, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(rapecontrol, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Rape[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
rapecontrol <- filter(controllimits, Crime == "Rape")
SimsAvg <- mean(sectionSPClist$Central$Rape[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Rape", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(rapecontrol, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(rapecontrol, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Rape[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```


Burglary {data-navmenu="Property Crime"} 
======================================================================

> Burglary

Row
------------------------------------------------------------------------------

### Section comparison

```{r burgtable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Burg[[4]],
                             sectionSPClist$Genesee$Burg[[4]],
                             sectionSPClist$Goodman$Burg[[4]],
                             sectionSPClist$Clinton$Burg[[4]],
                             sectionSPClist$Central$Burg[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Burg[[2]],
                                sectionSPClist$Genesee$Burg[[2]],
                                sectionSPClist$Goodman$Burg[[2]],
                                sectionSPClist$Clinton$Burg[[2]],
                                sectionSPClist$Central$Burg[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Burg[[3]],
                                    sectionSPClist$Genesee$Burg[[3]],
                                    sectionSPClist$Goodman$Burg[[3]],
                                    sectionSPClist$Clinton$Burg[[3]],
                                    sectionSPClist$Central$Burg[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r burgmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Burg,
                geneseeSPC = sectionSPClist$Genesee$Burg,
                goodmanSPC = sectionSPClist$Goodman$Burg,
                clintonSPC = sectionSPClist$Clinton$Burg,
                centralSPC = sectionSPClist$Central$Burg,
                linkhash = "#burglary-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
burgcontrol <- filter(controllimits, Crime == "Burglary")
SimsAvg <- mean(sectionSPClist$Lake$Burg[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Burglary") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- burgcontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Burglary") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- burgcontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Burglary", Section == 1), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(burgcontrol, Section == 'Lake'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(burgcontrol, Section == 'Lake'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Burg[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Genesee

```{r}
burgcontrol <- filter(controllimits, Crime == "Burglary")
SimsAvg <- mean(sectionSPClist$Genesee$Burg[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Burglary", Section == 3), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(burgcontrol, Section == 'Genesee'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(burgcontrol, Section == 'Genesee'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Burg[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
burgcontrol <- filter(controllimits, Crime == "Burglary")
SimsAvg <- mean(sectionSPClist$Goodman$Burg[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Burglary", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(burgcontrol, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(burgcontrol, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Burg[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
burgcontrol <- filter(controllimits, Crime == "Burglary")
SimsAvg <- mean(sectionSPClist$Clinton$Burg[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Burglary", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(burgcontrol, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(burgcontrol, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Burg[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
burgcontrol <- filter(controllimits, Crime == "Burglary")
SimsAvg <- mean(sectionSPClist$Central$Burg[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Burglary", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(burgcontrol, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(burgcontrol, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Burg[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```


Larceny {data-navmenu="Property Crime"} 
======================================================================

> Larceny

Row
------------------------------------------------------------------------------

### Section comparison

```{r larcenytable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Larc[[4]],
                             sectionSPClist$Genesee$Larc[[4]],
                             sectionSPClist$Goodman$Larc[[4]],
                             sectionSPClist$Clinton$Larc[[4]],
                             sectionSPClist$Central$Larc[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Larc[[2]],
                                sectionSPClist$Genesee$Larc[[2]],
                                sectionSPClist$Goodman$Larc[[2]],
                                sectionSPClist$Clinton$Larc[[2]],
                                sectionSPClist$Central$Larc[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Larc[[3]],
                                    sectionSPClist$Genesee$Larc[[3]],
                                    sectionSPClist$Goodman$Larc[[3]],
                                    sectionSPClist$Clinton$Larc[[3]],
                                    sectionSPClist$Central$Larc[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r larcmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Larc,
                geneseeSPC = sectionSPClist$Genesee$Larc,
                goodmanSPC = sectionSPClist$Goodman$Larc,
                clintonSPC = sectionSPClist$Clinton$Larc,
                centralSPC = sectionSPClist$Central$Larc,
                linkhash = "#larceny-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
larccontrol <- filter(controllimits, Crime == "Larceny")
SimsAvg <- mean(sectionSPClist$Lake$Larc[[5]]$Value)

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Larceny") %>% 
    select(Counts) %>%
    as.numeric()
maxlim <- larccontrol %>% 
    select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
ymax <- max(maxhist, maxlim) * 1.1

minhist <- mins %>% 
    filter(CrimeType == "Larceny") %>% 
    select(Counts) %>% 
    as.numeric()
minlim <- larccontrol %>% 
    top_n(1, -LowerLimit) %>% 
    select(LowerLimit) %>%
    distinct() %>% 
    as.numeric()
#ymin <- min(minhist, minlim)
ymin <- 0

p <- ggplot(filter(histdata, CrimeType == "Larceny", Section == 1), aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(larccontrol, Section == 'Lake'), aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(larccontrol, Section == 'Lake'), aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Lake$Larc[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```


### Genesee

```{r}
larccontrol <- filter(controllimits, Crime == "Larceny")
SimsAvg <- mean(sectionSPClist$Genesee$Larc[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Larceny", Section == 3), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(larccontrol, Section == 'Genesee'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(larccontrol, Section == 'Genesee'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Genesee$Larc[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Goodman

```{r}
larccontrol <- filter(controllimits, Crime == "Larceny")
SimsAvg <- mean(sectionSPClist$Goodman$Larc[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Larceny", Section == 5), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(larccontrol, Section == 'Goodman'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(larccontrol, Section == 'Goodman'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Goodman$Larc[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Clinton

```{r}
larccontrol <- filter(controllimits, Crime == "Larceny")
SimsAvg <- mean(sectionSPClist$Clinton$Larc[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Larceny", Section == 7), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(larccontrol, Section == 'Clinton'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(larccontrol, Section == 'Clinton'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Clinton$Larc[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```

### Central

```{r}
larccontrol <- filter(controllimits, Crime == "Larceny")
SimsAvg <- mean(sectionSPClist$Central$Larc[[5]]$Value)
p <- ggplot(filter(histdata, CrimeType == "Larceny", Section == 9), 
            aes(x = Yr, y = Counts)) +
    geom_line() +
    #geom_point() +
    theme_bw() +
    geom_line(data = filter(larccontrol, Section == 'Central'), 
              aes(x = Year, y = UpperLimit), linetype = "dashed") +
    geom_line(data = filter(larccontrol, Section == 'Central'), 
              aes(x = Year, y = LowerLimit), linetype = "dashed") +
    #scale_x_continuous(breaks = 2009:2019) +
    geom_point(data = sectionSPClist$Central$Larc[[5]], aes(x = curr.year, y = Value), alpha = .01) +
    geom_point(aes(x = curr.year, y = SimsAvg), shape = 16, size = 3, color = 'blue') +
    labs(x = "Year") +
    scale_y_continuous(limits = c(ymin, ymax)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank())
ggplotly(p, tooltip = c("Yr", "Counts", "SimsAvg"))
```
