---
title: "Patrol Divison Overview, as of `r format(Sys.Date() - 4, '%d %B, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    logo: //cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/RPDLogoSMALL.png
    orientation: row
    vertical_layout: fill
    theme: cerulean
---

```{r loaddata}

curr.year <- as.numeric(format(Sys.Date(), '%Y')) ### This current year to automatically reference the current year
begindate <- paste0(curr.year, '-01-01') ### For CFS to automatically create the begindate based on current year

library(stringr)
library(knitr)
library(flexdashboard)
library(RColorBrewer)
library(plotly)
library(leaflet)
library(reshape2)
library(jsonlite)
library(DT)
library(RODBC)
library(mapview) #for cool popups
library(leaflet.extras) #for popups in GeoJSON objects
library(tidyverse)

source("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Functions/LERMS_incidents.R")
source("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Functions/SPC.R")
source("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Functions/pullMCUdata.R")
source("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Functions/loadshootingvictims.R")

overviewmapfunc <- function(daddyJSON, 
                            lakeSPC, 
                            geneseeSPC, 
                            goodmanSPC, 
                            clintonSPC, 
                            centralSPC,
                            linkhash,
                            citymap,
                            sec) {
    babyJSON <- daddyJSON
    crimediff <- data_frame("Section" = sec,
                            "Difference" = c(lakeSPC[[2]] - lakeSPC[[3]],
                                             geneseeSPC[[2]] - geneseeSPC[[3]],
                                             goodmanSPC[[2]] - goodmanSPC[[3]],
                                             clintonSPC[[2]] - clintonSPC[[3]],
                                             centralSPC[[2]] - centralSPC[[3]])
                            ) %>%
        mutate(fillOpacity = abs(Difference / 100),
               fillColor = case_when(.$Difference > 0 ~ "Red",
                                     .$Difference < 0 ~ "Green",
                                     TRUE ~ "White"))
    
    crimediff <- crimediff[match(lapply(babyJSON$features, 
                                        function(x) x$properties$Section) %>% 
                                     unlist(), 
                                 crimediff$Section),]
    babyJSON$features <- lapply(
        babyJSON$features, function(x) {
            x$properties$style <- list(
                fillColor = crimediff$fillColor[which(
                    crimediff$Section == x$properties$Section)],
                fillOpacity = crimediff$fillOpacity[which(
                    crimediff$Section == x$properties$Section)]
            )
            x
        }
    )
    
    links <- data_frame(Section = sec,
                        link = c(paste0('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/LakeCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Lake Section Dashboard</a>'), 
                                 paste0('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/GeneseeCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Genesee Section Dashboard</a>'), 
                                 paste0('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/GoodmanCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Goodman Section Dashboard</a>'), 
                                 paste0('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/ClintonCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Clinton Section Dashboard</a>'), 
                                 paste0('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/CentralCrimeDashboard.html',
                                       linkhash, 
                                       '" target="_blank">Central Section Dashboard</a>')))
    
    babyJSON$features <- lapply(babyJSON$features, function(x) {
        
        x$properties$popup = links$link[which(links$Section == x$properties$Section)]
        x
    })
    
    return(citymap %>%
               addGeoJSON(
                   babyJSON
               ) %>%
               addGeoJSONv2(
                   babyJSON,
                   fillOpacity = 0,
                   popupProperty = "popup",
                   labelProperty = "Section",
                   highlightOptions = highlightOptions(color = 'white', weight = 10, bringToFront = TRUE)
               ))
    
}

projectionplot <- function(
    sectionname = "",
    sectionnumber = "",
    whichcrimetype = "",
    SPCcrimetype = "",
    controllimits = controllimits,
    histdata = histdata,
    ymax = 1000,
    ymin = 0) {
    
    control = filter(controllimits, Crime == whichcrimetype & Section == sectionname)
    
    p <- plot_ly(
        data = filter(histdata, CrimeType == whichcrimetype, Section == sectionnumber),
        type = "scatter",
        mode = "lines",
        x = ~Yr,
        y = ~Counts,
        name = "Historical",
        hoverinfo = "name",
        showlegend = FALSE) %>%
        add_trace(
            data = filter(control, Crime == whichcrimetype & Section == sectionname),
            x = ~Year,
            y = ~UpperLimit,
            showlegend = FALSE,
            name = "Upper Action Limit",
            hoverinfo = "name",
            line = list(dash = "dash", color = "Black")) %>%
        add_trace(
            data = filter(control, Crime == whichcrimetype & Section == sectionname),
            x = ~Year,
            y = ~LowerLimit,
            showlegend = FALSE,
            name = "Lower Action Limit",
            hoverinfo = "name",
            line = list(dash = "dash", color = "Black")) %>%
        add_trace(
            type = "scatter",
            mode = "markers",
            data = sectionSPClist[[sectionname]][[SPCcrimetype]][[5]],
            x = ~curr.year,
            y = ~Value,
            opacity = .1,
            color = I("Black"),
            name = "Simulations",
            hoverinfo = "name") %>%
        add_trace(
            type = "scatter",
            mode = "markers",
            x = curr.year,
            y = mean(sectionSPClist[[sectionname]][[SPCcrimetype]][[5]]$Value),
            name = "Average Sim",
            hoverinfo = "name+y",
            marker = list(size = 10, color = "blue")) %>%
        layout(xaxis = list(title = "", autotick = FALSE),
               yaxis = list(title = "", range = c(ymin, ymax)))
    
    return(p)
}



simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), tolower(substring(s, 2)),
      sep="", collapse=" ")
}

daddyJSON <- readLines("https://opendata.arcgis.com/datasets/772f3621fa354ec9abf3ba33f3ace59e_0.geojson") %>%
    paste(collapse = "\n") %>%
    fromJSON(simplifyVector = FALSE)
#gather section names and set color palettes for sections and beats
secNames <- sapply(daddyJSON$features, function(x) x$properties$Section)
sectionpal <- colorFactor(palette = colorspace::sequential_hcl(5),
                          domain = secNames)

citymap <- readRDS(file = "//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/citymap.RDS")
#old fitbounds: fitBounds(lng1 = -77.55, lat1 = 43.11, lng2 = -77.668684, lat2 = 43.264020)

#sevenDayGroupTable is a lookup table to get the current week (Group) from the date
#Because it uses length(Date) from seq.Date, it should work even in leap years

sevenDayGroupTable <- data.frame(Date = seq.Date(from = as.Date(begindate),
                                                 to = as.Date(paste0(curr.year, "-12-31")),
                                                 by = 1)) %>%
    mutate(DOY = 1:length(Date),
           Group = c(rep(1:51, each = 7), 
                     rep(52, times = length(Date) - 357)))

curr.week <- sevenDayGroupTable$Group[match(as.numeric(format(Sys.Date(), 
                                                             '%j')), 
                                           sevenDayGroupTable$DOY)] - 1

firearm.desc <- trimws(c('Prohibited Use of Weapon City Limits', 
                        'Use of Dangerous Weapon', 
                        'Criminal Use Firearm 1st: Commit Violent Class B Felony', 
                        'Discharges Loaded Firearm', 
                        'Use Firearm 1st: Possess a Deadly Weapon-Loaded',
                        'Criminal Use Firearm 2nd: Possess Deadly Weapon: Loaded', 
                        'Use Firearm 1st: Display Firearm', 
                        'Criminal Use Firearm 2nd: Display Firearm'))

firearmCrimeTypes <- c("Aggravated Assault", "Robbery", "Homicide", "Rape", "Simple Assault")

#load in RPD's crime data

df <- readRDS(file = "//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/citywidedf.RDS")

#use beatNames to make factor levels for beats
beatNames <- df %>%
    dplyr::select(GEOBeat) %>%
    unique() %>% 
    filter(! grepl(x = GEOBeat, pattern = "\\*")) %>% #remove *** as a beat name
    arrange(substr(GEOBeat, 3, 3), GEOBeat) %>%
    mutate(GEOBeat = as.factor(GEOBeat)) #this keeps *** as a factor level

CPWs <- df %>% filter(CrimeType == "Dangerous Weapons" & 
                          !trimws(Description) %in% firearm.desc &
                          as.numeric(WeaponIBRValue) < 11) %>%
    mutate(OccurFromDate = as.character(OccurFromDate)) #for table display purposes

crimes <- c('Aggravated Assault', 'Arson', 'Burglary', 'Homicide', 'Larceny', 'MV Theft', 'Rape', 'Robbery', 'Firearm')
sec <- c('Lake', 'Genesee', 'Goodman', 'Clinton', 'Central')

pal <- brewer.pal(name = "Reds", n = 9)

PropVals <- read.csv("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/ProportionsAndCounts.csv",
                     header= T)
ShootingControlLimits <- read.csv("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/3YrWeightedControlLimitsShootings.csv")
ShootingProps <- read.csv("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/ProportionsAndCountsShootings.csv",
                          stringsAsFactors = FALSE)
ShootingPropsFull <- ShootingProps

histdata <- read.csv(file = "//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/historicaldata.csv",
                     stringsAsFactors = FALSE,
                     header = TRUE)

controllimits <- read.csv(file = "//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/3YrWeightedControlLimits.csv", 
                       header = TRUE)

controllimits <- rbind(data.frame(controllimits, Year = 2017),
                    data.frame(controllimits, Year = 2018),
                    data.frame(controllimits, Year = 2019))

```


```{r loadSPC}

sectionSPClist <- readRDS("//cor.local/RPD/Chief/OBI/Projects/dashboard/RPDCrimeDashboard/Objects/sectionSPClist.RDS")

```

```{r ylims}

mins <- histdata %>% 
    group_by(CrimeType) %>% 
    filter(Counts == min(Counts)) %>%
    ungroup() %>%
    dplyr::select(-Yr) %>%
    distinct()

maxes <- histdata %>% 
    group_by(CrimeType) %>% 
    filter(Counts == max(Counts)) %>%
    ungroup() %>%
    dplyr::select(-Yr) %>%
    distinct()

```

Firearm Crime {data-navmenu="Violent Crime"} 
======================================================================

> Firearm Crime

Row
------------------------------------------------------------------------------

### Section comparison

```{r firearmtable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Firearm[[4]],
                             sectionSPClist$Genesee$Firearm[[4]],
                             sectionSPClist$Goodman$Firearm[[4]],
                             sectionSPClist$Clinton$Firearm[[4]],
                             sectionSPClist$Central$Firearm[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Firearm[[2]],
                                sectionSPClist$Genesee$Firearm[[2]],
                                sectionSPClist$Goodman$Firearm[[2]],
                                sectionSPClist$Clinton$Firearm[[2]],
                                sectionSPClist$Central$Firearm[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Firearm[[3]],
                                    sectionSPClist$Genesee$Firearm[[3]],
                                    sectionSPClist$Goodman$Firearm[[3]],
                                    sectionSPClist$Clinton$Firearm[[3]],
                                    sectionSPClist$Central$Firearm[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))
```

### Map

```{r Firearmcrimemap}

firearmsJSON <- daddyJSON

firearmdiff <- data_frame("Section" = sec,
                          "Difference" = c(sectionSPClist$Lake$Firearm[[2]] - sectionSPClist$Lake$Firearm[[3]],
                                           sectionSPClist$Genesee$Firearm[[2]] - sectionSPClist$Genesee$Firearm[[3]],
                                           sectionSPClist$Goodman$Firearm[[2]] - sectionSPClist$Goodman$Firearm[[3]],
                                           sectionSPClist$Clinton$Firearm[[2]] - sectionSPClist$Clinton$Firearm[[3]],
                                           sectionSPClist$Central$Firearm[[2]] - sectionSPClist$Central$Firearm[[3]])) %>%
    mutate(fillOpacity = abs(Difference / 100),
           fillColor = case_when(.$Difference > 0 ~ "Red",
                             .$Difference < 0 ~ "Green",
                             TRUE ~ "White"))
firearmdiff <- firearmdiff[match(lapply(firearmsJSON$features, function(x) x$properties$Section) %>% 
                                     unlist(), 
                                 firearmdiff$Section),]

firearmsJSON$features <- lapply(firearmsJSON$features, function(x) {
    x$properties$style <- list(
        fillColor = firearmdiff$fillColor[which(firearmdiff$Section == x$properties$Section)],
        fillOpacity = firearmdiff$fillOpacity[which(firearmdiff$Section == x$properties$Section)]
    )
    x
})

links <- data_frame(Section = sec,
                    link = c('<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/LakeCrimeDashboard.html#firearm-crime-1" target="_blank">Lake Section Dashboard</a>', 
                             '<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/GeneseeCrimeDashboard.html#firearm-crime-1" target="_blank">Genesee Section Dashboard</a>', 
                             '<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/GoodmanCrimeDashboard.html#firearm-crime-1" target="_blank">Goodman Section Dashboard</a>', 
                             '<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/ClintonCrimeDashboard.html#firearm-crime-1" target="_blank">Clinton Section Dashboard</a>', 
                             '<a href="file://cor.local/MCAC/Department/MCAC Operations/Crime Dashboards/CentralCrimeDashboard.html#firearm-crime-1" target="_blank">Central Section Dashboard</a>'))


firearmsJSON$features <- lapply(firearmsJSON$features, function(x) {
    
    x$properties$popup = links$link[which(links$Section == x$properties$Section)]
    x
})

citymap %>%
    addGeoJSON(
        firearmsJSON
        ) %>%
    addGeoJSONv2(
        firearmsJSON
        , fillOpacity = 0
        , popupProperty = "popup"
        , labelProperty = "Section"
        , highlightOptions = highlightOptions(color = "white", weight = 10, bringToFront = TRUE)
        )

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Firearm") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>% 
    filter(Crime == "Firearm") %>%
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
firearmymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Firearm", SPCcrimetype = "Firearm",
               histdata = histdata,
               controllimits = controllimits, ymax = firearmymax, ymin = 0)

```

### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Firearm", SPCcrimetype = "Firearm",
               histdata = histdata,
               controllimits = controllimits, ymax = firearmymax, ymin = 0)
```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Firearm", SPCcrimetype = "Firearm",
               histdata = histdata,
               controllimits = controllimits, ymax = firearmymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Firearm", SPCcrimetype = "Firearm",
               histdata = histdata,
               controllimits = controllimits, ymax = firearmymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Firearm", SPCcrimetype = "Firearm",
               histdata = histdata,
               controllimits = controllimits, ymax = firearmymax, ymin = 0)
```

Shooting Victims{data-navmenu="Violent Crime"} 
======================================================================

> Shooting Victims

Row
------------------------------------------------------------------------------

### Section comparison

```{r shootingvictimstables}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$SV[[4]],
                             sectionSPClist$Genesee$SV[[4]],
                             sectionSPClist$Goodman$SV[[4]],
                             sectionSPClist$Clinton$SV[[4]],
                             sectionSPClist$Central$SV[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$SV[[2]],
                                sectionSPClist$Genesee$SV[[2]],
                                sectionSPClist$Goodman$SV[[2]],
                                sectionSPClist$Clinton$SV[[2]],
                                sectionSPClist$Central$SV[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$SV[[3]],
                                    sectionSPClist$Genesee$SV[[3]],
                                    sectionSPClist$Goodman$SV[[3]],
                                    sectionSPClist$Clinton$SV[[3]],
                                    sectionSPClist$Central$SV[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r svmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$SV,
                geneseeSPC = sectionSPClist$Genesee$SV,
                goodmanSPC = sectionSPClist$Goodman$SV,
                clintonSPC = sectionSPClist$Clinton$SV,
                centralSPC = sectionSPClist$Central$SV,
                linkhash = "#shooting-victims-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Shooting") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- ShootingControlLimits %>% 
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
shootingymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Shooting", SPCcrimetype = "SV",
               histdata = histdata,
               controllimits = ShootingControlLimits %>%
                   mutate(Crime = "Shooting"), 
               ymax = shootingymax, ymin = 0)

```

### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Shooting", SPCcrimetype = "SV",
               histdata = histdata,
               controllimits = ShootingControlLimits %>%
                   mutate(Crime = "Shooting"), 
               ymax = shootingymax, ymin = 0)
```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Shooting", SPCcrimetype = "SV",
               histdata = histdata,
               controllimits = ShootingControlLimits %>%
                   mutate(Crime = "Shooting"), 
               ymax = shootingymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Shooting", 
               SPCcrimetype = "SV",
               histdata = histdata,
               controllimits = ShootingControlLimits %>%
                   mutate(Crime = "Shooting"), 
               ymax = shootingymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Shooting", 
               SPCcrimetype = "SV",
               histdata = histdata,
               controllimits = ShootingControlLimits %>%
                   mutate(Crime = "Shooting"), 
               ymax = shootingymax, ymin = 0)
```

Robbery {data-navmenu="Violent Crime"} 
======================================================================

> Robbery

Row
------------------------------------------------------------------------------

### Section comparison

```{r robberytable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Rob[[4]],
                             sectionSPClist$Genesee$Rob[[4]],
                             sectionSPClist$Goodman$Rob[[4]],
                             sectionSPClist$Clinton$Rob[[4]],
                             sectionSPClist$Central$Rob[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Rob[[2]],
                                sectionSPClist$Genesee$Rob[[2]], 
                                sectionSPClist$Goodman$Rob[[2]], 
                                sectionSPClist$Clinton$Rob[[2]], 
                                sectionSPClist$Central$Rob[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Rob[[3]],
                                    sectionSPClist$Genesee$Rob[[3]],
                                    sectionSPClist$Goodman$Rob[[3]],
                                    sectionSPClist$Clinton$Rob[[3]],
                                    sectionSPClist$Central$Rob[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```                         

### Map

```{r robmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Rob,
                geneseeSPC = sectionSPClist$Genesee$Rob,
                goodmanSPC = sectionSPClist$Goodman$Rob,
                clintonSPC = sectionSPClist$Clinton$Rob,
                centralSPC = sectionSPClist$Central$Rob,
                linkhash = "#robbery-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}
#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Robbery") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>%
    filter(Crime == "Robbery") %>% 
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
Robymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Robbery", SPCcrimetype = "Rob",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = Robymax, ymin = 0)

```

### Genesee

```{r}

projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Robbery", SPCcrimetype = "Rob",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = Robymax, ymin = 0)

```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Robbery", SPCcrimetype = "Rob",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = Robymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Robbery", SPCcrimetype = "Rob",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = Robymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Robbery", SPCcrimetype = "Rob",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = Robymax, ymin = 0)
```

Aggravated Assaults {data-navmenu="Violent Crime"} 
======================================================================

> Aggravated Assaults

Row
------------------------------------------------------------------------------

### Section comparison

```{r aggassaulttable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Aslt[[4]],
                             sectionSPClist$Genesee$Aslt[[4]],
                             sectionSPClist$Goodman$Aslt[[4]],
                             sectionSPClist$Clinton$Aslt[[4]],
                             sectionSPClist$Central$Aslt[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Aslt[[2]],
                                sectionSPClist$Genesee$Aslt[[2]],
                                sectionSPClist$Goodman$Aslt[[2]],
                                sectionSPClist$Clinton$Aslt[[2]],
                                sectionSPClist$Central$Aslt[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Aslt[[3]],
                                    sectionSPClist$Genesee$Aslt[[3]],
                                    sectionSPClist$Goodman$Aslt[[3]],
                                    sectionSPClist$Clinton$Aslt[[3]],
                                    sectionSPClist$Central$Aslt[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r asltmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Aslt,
                geneseeSPC = sectionSPClist$Genesee$Aslt,
                goodmanSPC = sectionSPClist$Goodman$Aslt,
                clintonSPC = sectionSPClist$Clinton$Aslt,
                centralSPC = sectionSPClist$Central$Aslt,
                linkhash = "#aggravated-assault-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Aggravated Assault") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>% 
    filter(Crime == "Aggravated Assault") %>%
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
asltymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Aggravated Assault", SPCcrimetype = "Aslt",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = asltymax, ymin = 0)


```

### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Aggravated Assault", SPCcrimetype = "Aslt",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = asltymax, ymin = 0)
```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Aggravated Assault", SPCcrimetype = "Aslt",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = asltymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Aggravated Assault", SPCcrimetype = "Aslt",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = asltymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Aggravated Assault", SPCcrimetype = "Aslt",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = asltymax, ymin = 0)
```


Homicide {data-navmenu="Violent Crime"} 
======================================================================

> Homicide

Row
------------------------------------------------------------------------------

### Section comparison

```{r homicidetable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Homicide[[4]],
                             sectionSPClist$Genesee$Homicide[[4]],
                             sectionSPClist$Goodman$Homicide[[4]],
                             sectionSPClist$Clinton$Homicide[[4]],
                             sectionSPClist$Central$Homicide[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Homicide[[2]],
                                sectionSPClist$Genesee$Homicide[[2]],
                                sectionSPClist$Goodman$Homicide[[2]],
                                sectionSPClist$Clinton$Homicide[[2]],
                                sectionSPClist$Central$Homicide[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Homicide[[3]],
                                    sectionSPClist$Genesee$Homicide[[3]],
                                    sectionSPClist$Goodman$Homicide[[3]],
                                    sectionSPClist$Clinton$Homicide[[3]],
                                    sectionSPClist$Central$Homicide[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r hommap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Homicide,
                geneseeSPC = sectionSPClist$Genesee$Homicide,
                goodmanSPC = sectionSPClist$Goodman$Homicide,
                clintonSPC = sectionSPClist$Clinton$Homicide,
                centralSPC = sectionSPClist$Central$Homicide,
                linkhash = "#homicide-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Homicide") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>%
    filter(Crime == "Homicide") %>% 
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
homymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Homicide", SPCcrimetype = "Homicide",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = homymax, ymin = 0)

```

### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Homicide", SPCcrimetype = "Homicide",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = homymax, ymin = 0)
```

### Goodman

```{r}

projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Homicide", SPCcrimetype = "Homicide",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = homymax, ymin = 0)

```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Homicide", SPCcrimetype = "Homicide",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = homymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Homicide", SPCcrimetype = "Homicide",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = homymax, ymin = 0)

```

Rape {data-navmenu="Violent Crime"} 
======================================================================

> Rape

Row
------------------------------------------------------------------------------

### Section comparison

```{r rapetable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Rape[[4]],
                             sectionSPClist$Genesee$Rape[[4]],
                             sectionSPClist$Goodman$Rape[[4]],
                             sectionSPClist$Clinton$Rape[[4]],
                             sectionSPClist$Central$Rape[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Rape[[2]],
                                sectionSPClist$Genesee$Rape[[2]],
                                sectionSPClist$Goodman$Rape[[2]],
                                sectionSPClist$Clinton$Rape[[2]],
                                sectionSPClist$Central$Rape[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Rape[[3]],
                                    sectionSPClist$Genesee$Rape[[3]],
                                    sectionSPClist$Goodman$Rape[[3]],
                                    sectionSPClist$Clinton$Rape[[3]],
                                    sectionSPClist$Central$Rape[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r rapemap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Rape,
                geneseeSPC = sectionSPClist$Genesee$Rape,
                goodmanSPC = sectionSPClist$Goodman$Rape,
                clintonSPC = sectionSPClist$Clinton$Rape,
                centralSPC = sectionSPClist$Central$Rape,
                linkhash = "#rape-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Rape") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>% 
    filter(Crime == "Rape") %>%
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
rapeymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Rape", SPCcrimetype = "Rape",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = rapeymax, ymin = 0)

```

### Genesee

```{r}

projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Rape", SPCcrimetype = "Rape",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = rapeymax, ymin = 0)
```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Rape", SPCcrimetype = "Rape",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = rapeymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Rape", SPCcrimetype = "Rape",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = rapeymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Rape", SPCcrimetype = "Rape",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = rapeymax, ymin = 0)
```


Burglary {data-navmenu="Property Crime"} 
======================================================================

> Burglary

Row
------------------------------------------------------------------------------

### Section comparison

```{r burgtable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Burg[[4]],
                             sectionSPClist$Genesee$Burg[[4]],
                             sectionSPClist$Goodman$Burg[[4]],
                             sectionSPClist$Clinton$Burg[[4]],
                             sectionSPClist$Central$Burg[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Burg[[2]],
                                sectionSPClist$Genesee$Burg[[2]],
                                sectionSPClist$Goodman$Burg[[2]],
                                sectionSPClist$Clinton$Burg[[2]],
                                sectionSPClist$Central$Burg[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Burg[[3]],
                                    sectionSPClist$Genesee$Burg[[3]],
                                    sectionSPClist$Goodman$Burg[[3]],
                                    sectionSPClist$Clinton$Burg[[3]],
                                    sectionSPClist$Central$Burg[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r burgmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Burg,
                geneseeSPC = sectionSPClist$Genesee$Burg,
                goodmanSPC = sectionSPClist$Goodman$Burg,
                clintonSPC = sectionSPClist$Clinton$Burg,
                centralSPC = sectionSPClist$Central$Burg,
                linkhash = "#burglary-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Burglary") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>% 
    filter(Crime == "Burglary") %>%
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
burgymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Burglary", SPCcrimetype = "Burg",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = burgymax, ymin = 0)

```

### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Burglary", SPCcrimetype = "Burg",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = burgymax, ymin = 0)
```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Burglary", SPCcrimetype = "Burg",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = burgymax, ymin = 0)
```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Burglary", SPCcrimetype = "Burg",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = burgymax, ymin = 0)
```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Burglary", SPCcrimetype = "Burg",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = burgymax, ymin = 0)
```


Larceny {data-navmenu="Property Crime"} 
======================================================================

> Larceny

Row
------------------------------------------------------------------------------

### Section comparison

```{r larcenytable}

tab <- data.frame(Sections = sec,
                  Counts = c(sectionSPClist$Lake$Larc[[4]],
                             sectionSPClist$Genesee$Larc[[4]],
                             sectionSPClist$Goodman$Larc[[4]],
                             sectionSPClist$Clinton$Larc[[4]],
                             sectionSPClist$Central$Larc[[4]]),
                  RiskOfRed = c(sectionSPClist$Lake$Larc[[2]],
                                sectionSPClist$Genesee$Larc[[2]],
                                sectionSPClist$Goodman$Larc[[2]],
                                sectionSPClist$Clinton$Larc[[2]],
                                sectionSPClist$Central$Larc[[2]]),
                  ChanceOfGreen = c(sectionSPClist$Lake$Larc[[3]],
                                    sectionSPClist$Genesee$Larc[[3]],
                                    sectionSPClist$Goodman$Larc[[3]],
                                    sectionSPClist$Clinton$Larc[[3]],
                                    sectionSPClist$Central$Larc[[3]]))

datatable(tab,
          rownames = FALSE,
          colnames = c("Sections", 
                       "YTD Totals", 
                       "% chance of exceeding upper action limit", 
                       "% chance of beating lower action limit"),
          options = list(dom = 'tf',
                         columnDefs = list(list(className = 'dt-right', targets = 0:3))))

```

### Map

```{r larcmap}

overviewmapfunc(daddyJSON = daddyJSON,
                lakeSPC = sectionSPClist$Lake$Larc,
                geneseeSPC = sectionSPClist$Genesee$Larc,
                goodmanSPC = sectionSPClist$Goodman$Larc,
                clintonSPC = sectionSPClist$Clinton$Larc,
                centralSPC = sectionSPClist$Central$Larc,
                linkhash = "#larceny-1",
                citymap = citymap,
                sec = sec)

```

Row {data-height=30}
------------------------------------------------------------------------------

`r paste0("Historical Year-End Totals (2009 - ", curr.year - 1, ") with Current Year Projections")`

Row {data-height=250}
------------------------------------------------------------------------------

### Lake

```{r}

#set y axis limits
maxhist <- maxes %>% 
    filter(CrimeType == "Larceny") %>% 
    dplyr::select(Counts) %>%
    as.numeric()
maxlim <- controllimits %>% 
    filter(Crime == "Larceny") %>%
    dplyr::select(UpperLimit) %>% 
    top_n(1, UpperLimit) %>% 
    distinct() %>% 
    as.numeric()
larcymax <- max(maxhist, maxlim) * 1.1

projectionplot(sectionname = "Lake", sectionnumber = 1, 
               whichcrimetype = "Larceny", SPCcrimetype = "Larc",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = larcymax, ymin = 0)

```


### Genesee

```{r}
projectionplot(sectionname = "Genesee", sectionnumber = 3, 
               whichcrimetype = "Larceny", SPCcrimetype = "Larc",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = larcymax, ymin = 0)

```

### Goodman

```{r}
projectionplot(sectionname = "Goodman", sectionnumber = 5, 
               whichcrimetype = "Larceny", SPCcrimetype = "Larc",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = larcymax, ymin = 0)

```

### Clinton

```{r}
projectionplot(sectionname = "Clinton", sectionnumber = 7, 
               whichcrimetype = "Larceny", SPCcrimetype = "Larc",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = larcymax, ymin = 0)

```

### Central

```{r}
projectionplot(sectionname = "Central", sectionnumber = 9, 
               whichcrimetype = "Larceny", SPCcrimetype = "Larc",
               histdata = histdata,
               controllimits = controllimits, 
               ymax = larcymax, ymin = 0)

```
